Journal and article coverage

### 2025-03-06 analysis/manuscript.qmd
Starting replication

>>>>

## Replication

This section examines the open access uptake in hybrid journals, focusing on the influence of transformative agreements across hoaddata, Scopus and Web of Science.
A key objective of this analysis is to determine whether consistent results can be derived across these three data sources, despite their differing coverage and methodologies. 
By identifying potential variations, this study evaluates the suitability of open data approaches, such as hoaddata, as alternatives to proprietary bibliometric databases like Scopus and Web of Science.

Following @Jahn_2025, the impact of transformative agreements on hybrid open access is assessed by analysing the proportion of open access articles, both overall and those specifically enabled by transformative agreements. 
The analysis covers the publication years 2019 to 2023, providing insights into temporal trends in the adoption of transformative agreements and their influence on open access in hybrid journals.
The analysis will present breakdowns by publishers and countries.

A complicating factor in the comparision is the differing coverage of author affiliation data across the datasets.
In hoaddata, which relies on OpenAlex for affiliation information, the lack of comprehensive corresponding author data restricts the analysis to first authors when estimating the influence of transformative agreements. 
In contrast, Scopus and Web of Science provide more robust coverage of corresponding author affiliations, enabling a comparative assessment of how authorship roles--first versus corresponding authors--influence estimates of open access funding through transformative agreements.

### 2025-03-06 analysis/manuscript.tex
Starting replication

>>>>

\subsection{Replication}\label{replication}

This section examines the open access uptake in hybrid journals,
focusing on the influence of transformative agreements across hoaddata,
Scopus and Web of Science. A key objective of this analysis is to
determine whether consistent results can be derived across these three
data sources, despite their differing coverage and methodologies. By
identifying potential variations, this study evaluates the suitability
of open data approaches, such as hoaddata, as alternatives to
proprietary bibliometric databases like Scopus and Web of Science.

Following Jahn (2025), the impact of transformative agreements on hybrid
open access is assessed by analysing the proportion of open access
articles, both overall and those specifically enabled by transformative
agreements. The analysis covers the publication years 2019 to 2023,
providing insights into temporal trends in the adoption of
transformative agreements and their influence on open access in hybrid
journals. The analysis will present breakdowns by publishers and
countries.

A complicating factor in the comparision is the differing coverage of
author affiliation data across the datasets. In hoaddata, which relies
on OpenAlex for affiliation information, the lack of comprehensive
corresponding author data restricts the analysis to first authors when
estimating the influence of transformative agreements. In contrast,
Scopus and Web of Science provide more robust coverage of corresponding
author affiliations, enabling a comparative assessment of how authorship
roles--first versus corresponding authors--influence estimates of open
access funding through transformative agreements.
